A Domain Specific Language for Functional Code Fusion for Intrusion Detection Algorithms in Wireless Sensor Networks

### 2014-09-23 paper.tex
added more references
updated affiliation + acknowledgements

\author{\IEEEauthorblockN{Christophe Van Ginneken, Jef Maerien, Christophe
Huygens, Danny Hughes, Wouter Joosen}%
\IEEEauthorblockA{iMinds - DistriNet - KU Leuven\\
B-3001, Leuven, Belgium\\
\{firstname.lastname\}@cs.kuleuven.be}}

@@

WSN

IDS as a non-functional cost

Economics of development

@@

@@

2 algorithms

TODO: add 3rd ?

@@

We would like to thank the reviewers for their thoughtful and helpful comments
that enhanced the readability of this paper. Our gratitude and respect also
goes out to all members of the NES task force at KU Leuven/DistriNet for
creating the nurturing environment where these ideas could grow.

>>>>

\author{\IEEEauthorblockN{Christophe Van Ginneken, Jef Maerien, Christophe
Huygens, Danny Hughes, Wouter Joosen}%
\IEEEauthorblockA{iMinds-DistriNet, KU Leuven\\
3001 Leuven, Belgium\\
\{firstname.lastname\}@cs.kuleuven.be}}

@@

WSN \cite{baggio2005wireless,werner2005monitoring,hughes2006gridstix}

Economics of development, IDS as a non-functional cost \cite{lee2002toward}

Energy in WSNs \cite{hughes2013energy}

@@

IDS in WSN \cite{perrig2004security,mishra2004intrusion}

DSL \cite{fowler2010domain,mernik2005and}

@@

2 algorithms \cite{ganeriwal2008reputation}

TODO: add 3rd ? \cite{krontiris2009cooperative}

@@

This research is partially funded by the Interuniversity Attraction Poles
Programme Belgian State, Belgian Science Policy, and by the Research Fund KU
Leuven. This research is partially funded by the EU FP7 project NESSoS. We
would like to thank the reviewers for their thoughtful and helpful comments
that enhanced the readability of this paper. Our gratitude and respect also
goes out to all members of the NES task force at KU Leuven/DistriNet for
creating the nurturing environment where these ideas could grow.
